Classifying Human Driving Behavior via Deep Neural Networks

### 2017-05-29 paper/paper-DrexelFormat.tex

Notice that as forward-propagation sends output of a layer as input of next layer, back-propagation sends error of a layer to previous layer. For example, the $\delta_i=\frac{\partial J}{\partial o'_i}$ is error on output layer then sends it to hidden layer.

>>>>

Notice that as forward-propagation sends output of a layer as input of the next layer, back-propagation sends the error of a the layer to the previous layer. For example, if the $\delta_i=\frac{\partial J}{\partial o'_i}$ is an error on the output layer, then it is sent to hidden layers.
